---
title: "Hw02"
output: github_document
---

```{r, message=FALSE}
require(gapminder)
```
View head of the dataset
```{r}
head(gapminder)
```

It's a list
```{r}
typeof(gapminder)
```
It's a dataframe
```{r}
class(gapminder)
```
How many columns?
```{r}
ncol(gapminder)
```
How many rows?
```{r}
nrow(gapminder)
```
`nrow` and `ncol` are more informative when writing for loops
```{r}
dim(gapminder)
```
What are the types of the variables?
```{r}
str(gapminder)
```
Possible values
```{r}
unique(gapminder$continent)
```
Africa is typical and the distribution is as follows
```{r}
ftable(gapminder$continent)
```
Spread and five-number summary
```{r}
summary(gapminder$lifeExp)
```
70~75 is typical
```{r}
hist(gapminder$lifeExp)
```
Histogram of a quantitative variable
```{r}
require(ggplot2)
plot <- ggplot(gapminder,aes(lifeExp))
plot + geom_histogram()
```
Frequency boxplot of a categorical variable
```{r}
plot+geom_bar(aes(continent))
```
Plot 3 variables altogether
```{r}
plot <- ggplot(gapminder,aes(lifeExp,year))
plot + geom_point(aes(size=pop))
```
A plot similar to above by multi-faceted 
```{r}
plot + geom_point(aes(size=pop)) + facet_wrap(~continent)
```
Pop into filter and select
```{r}
require(tidyverse)
gapminder %>%
  filter(country=="Afghanistan") %>% 
  select(pop,year) %>% 
  ggplot(.,aes(year,pop)) + geom_line()
```
No, since
```{r}
filter(gapminder, country == c("Rwanda", "Afghanistan"))
```
This is different from
```{r}
filter(gapminder, country == "Rwanda")
```
library(knitr)
```{r}
require(knitr)
kable(filter(gapminder, country %in% c("Rwanda", "Afghanistan")))
```

Exercise 7.3 frequency plot
```{r}
ggplot(gapminder, mapping = aes(x = lifeExp,colour = continent)) + 
  geom_freqpoly(binwidth = 5)
```
